\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}
\geometry{a4paper}
\title{Comprehensive Development Documentation}
\author{ilhamoeba22}
\date{2026-02-12}

\begin{document}
\maketitle

\section{System Architecture}
This section covers the overall architecture of the system, explaining the different components and their interactions. Include diagrams as needed.

\subsection{Component Overview}
- Component 1: Description...
- Component 2: Description...

\section{Database Design}
Describe the database schema, tables, and relationships.

\subsection{ER Diagram}
Provide an ER diagram image if available.

\subsection{Tables}
\begin{itemize}
  \item Table 1: Description...
  \item Table 2: Description...
\end{itemize}

\section{Workflow Logic}
Explain the workflow of the application, including state management and user interactions.

\section{API Routes}
List the API routes with their request types, paths, and descriptions.
\begin{itemize}
  \item \textbf{GET /api/resource}: Description of the resource...
  \item \textbf{POST /api/resource}: Description of the resource...
\end{itemize}

\section{Models}
Detail the data models used in the application.
\begin{itemize}
  \item Model 1: Description...
  \item Model 2: Description...
\end{itemize}

\section{Filament Pages}
Describe Filament pages, including their purpose and associated features.
\begin{itemize}
  \item Page 1: Description...
  \item Page 2: Description...
\end{itemize}

\section{Implementation Details}
Provide information about the implementation, environment setup, and deployment processes.
\begin{itemize}
  \item Step 1: Description...
  \item Step 2: Description...
\end{itemize}

\end{document}